No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-15 main/LICS.tex
finished draft intro

@@

In one of several possible definitions, a \emph{$\star$-autonomous category} \citep{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
%
\begin{itemize}

@@

\subsection{Proof nets}

@@

\begin{proposition}[\citeauthor{DR89}, \citeyear{DR89}]
\label{prop:correctness and sequentialisation}
%
For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
%
For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
%
\end{proposition}

@@

\begin{proposition}[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
\label{prop:proof nets work}
%
For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$ such that $\Pi\toNet\links$ and $\Pi'\toNet\links'$, $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
%
\end{proposition}

@@

\subsection{Notation}

@@

\subsection{Completeness}

@@

\subsection{Soundness}

>>>>

\subsection*{Constraint logic and reconfiguration problems}

The proof of the \textsc{pspace}-completeness result relies on a polynomial reduction from %the configuration--to--configuration problem in
\emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
%
It consists of a simple graph rewriting mechanism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied, and asks whether two graphs are related in a series of valid rewriting steps.

Constraint logic belongs to a class of problems called \emph{reconfiguration problems} \cite{ReconfigurationProblems}: can one solution to a given problem be transformed into another by a series of elementary changes, while remaining valid throughout?
%
For example, for boolean satisfyability (SAT) the reconfiguration problem asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
%
It is not uncommon for an \textsc{np}-complete problem to have an associated reconfiguration problem that is \textsc{pspace}-complete \cite{ReconfigurationProblems}; one example is SAT-reconfiguration, which is \textsc{pspace}-complete.

MLL proof equivalence may be usefully classified as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Lincoln-1994}.

@@

In one of several possible definitions, a \emph{$\star$-autonomous category} \cite{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
%
\begin{itemize}

@@

\subsection*{Proof nets}

@@

\begin{proposition}[\cite{DR89}]
\label{prop:correctness and sequentialisation}
%
For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
%
For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
%
\end{proposition}

@@

\begin{proposition}[\cite{HughesMLLProofNets}] %[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
\label{prop:proof nets work}
%
For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$ such that $\Pi\toNet\links$ and $\Pi'\toNet\links'$, $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
%
\end{proposition}

@@

\subsection*{Notation}

@@

\subsection*{Completeness}

@@

\subsection*{Soundness}
